---
title: "Munging Two"
output: html_notebook
---

This is my second attempt at munging the data. This time I'm going to try to make sure I use the right functions.
```{r}
(current_files <- list.files(pattern = '[a-zA-Z0-9_].csv'))
```
Now read the data in using tidyverse
```{r}
library(tidyverse)
all_data <- do.call("rbind", lapply(current_files, read_csv, col_names = c("participant", "food_rated", "food_rating", "trial_food_c", "trial_food_d", "decision", "opponent_decision", "rt", 'x'), skip=1, col_types = cols(
  participant = col_character(),
  food_rated = col_character(),
  food_rating = col_integer(),
  trial_food_c = col_character(),
  trial_food_d = col_character(),
  decision = col_character(),
  opponent_decision = col_character(),
  rt = col_double(),
  x = col_character()
)))
```
We had to specify a lot of things, but the advantage is that things have been read correctly.
```{r}
all_data
```
Now it's time to start processing the data. See munging1.rmd for some visualizations
```{r}
difference <- function(food_rating) {
  return (food_rating[1] - food_rating[2])
}
by_participant <- group_by(all_data, participant, food_rated)
food_change <- by_participant %>%
  summarise(food_change = difference(food_rating),
            original_rating = food_rating[1],
            final_rating = food_rating[2],
            avg_rating = mean(food_rating, na.rm = TRUE))
food_change
```
Separate the decision trials into its own tribble:
```{r}
decision_task <- all_data %>%
  filter(!is.na(trial_food_c)) %>%
  select(participant, trial_food_c, trial_food_d, decision, opponent_decision, rt) %>%
  group_by(participant)
```

```{r}
just_ratings <- filter(food_change,!is.na(original_rating))
```


Let's filter this to have the c_food
```{r}
d_task_with_rating <- decision_task %>% 
  left_join(just_ratings) %>%
  filter(trial_food_c == food_rated) %>%
  rename(c_change = food_change,
         c_rating = original_rating) %>%
  select(participant, trial_food_c, trial_food_d, decision, opponent_decision, c_change, c_rating)
```

Now let's get the d_food into the dataframe:
```{r}
d_task_with_rating <- d_task_with_rating %>% 
  left_join(just_ratings) %>%
  filter(trial_food_d == food_rated) %>%
  rename(d_change = food_change,
         d_rating = original_rating) %>%
  select(participant, trial_food_c, trial_food_d, decision, opponent_decision, c_change, c_rating, d_change, d_rating)
```
How often do we see changes if the participant defects?
```{r}
(defect_decision <- filter(d_task_with_rating, decision == 'D'))
mean(defect_decision$d_change)
mean(defect_decision$c_change)
(cooperate_decision <- filter(d_task_with_rating, decision == 'C'))
mean(cooperate_decision$d_change)
mean(cooperate_decision$c_change)
```
What if we can create a test of stats?
```{r}
d_task_with_rating$decision <- factor(d_task_with_rating$decision, labels = c("C", "D"))
d_task_with_rating.mod1 = lm(d_change ~ decision, data = d_task_with_rating)
d_task_with_rating.mod1
```

```{r}
anova(d_task_with_rating.mod1)
confint(d_task_with_rating.mod1)
```
How about the c_change?
```{r}
d_task_with_rating.mod2 = lm(c_change ~ decision, data = d_task_with_rating)
d_task_with_rating.mod2
anova(d_task_with_rating.mod2)
confint(d_task_with_rating.mod2)
```
Let's try this again, but let's do the mean of each participant change, to see if that makes a difference:
```{r}
participant_decision_summary <- d_task_with_rating %>%
  group_by(participant) %>%
  summarise(
    c_change_mean = mean(c_change),
    d_change_mean = mean(d_change)
    # Let's create a column for whether they are competitive or not
  )
participant_decision_summary
```

Now let's do the same statistical tests, but group based on... well, nvm.
```{r}
#participant_decision_summary.mod2 = lm(c_change_mean ~ decision, data = d_task_with_rating)
#d_task_with_rating.mod2
#anova(d_task_with_rating.mod2)
#confint(d_task_with_rating.mod2)
```





For the neural data, let's see if we can separate out the data based on low dissonance vs. high dissonance. How will we do it? Let's create a new column, consonance.
```{r}
(d_task_with_rating <-
  mutate(d_task_with_rating,
         consonance = d_rating - c_rating
         ))
```
Now group by participant and order based on consonance
```{r}
(consonance_task <- d_task_with_rating %>%
  group_by(participant) %>%
  arrange(participant, consonance))
```
Now let's get a median for each participant, and use that to split them in half and create a new column which just has two groups, high dissonance and low dissonance. That way we can try comparing them with reaction time using an ANOVA test.
```{r}

```